Are Delayed Issues Harder to Resolve? Revisiting Cost-to-Fix of Defects throughout the Lifecycle

### 2016-09-15 phaseDelay4Emse.tex
typo

Details:
\item Page 24:12 - "the cased study"
\item Page 7:24 - "Some studies that report less-than" Remove extra "that".
\item Page 12:41 - "quote elaborate" quite?
\item Page 14:30 - "the of the"
\item Page 14:45 - "complete submitted"
\item Page 15-16 - No thousands separators.
\item Page 16:48 - "only 25\% of the teams…" Was this supposed to be a separate item in the bullet list?
\item Page 18:51 - "raises" -\> "raised"

\begin{quote}{\em 
Reply 1.11: Fixed. Thanks!
}\end{quote}

@@

Reviewer #2: This revised version (R1) of the paper contains many corrections, changes, and enhancements. The authors have considered all the reviewer's comments and have provided precise responses. My own observations (i.e. Reviewer #2) have been globally satisfied, and thanks to comments from reviewers #1 and #3, the paper has been significantly enhanced.

@@

\item p3, line 1: "that" repeated

\item Section 5.2: the numbers about the TSP database can be regrouped in a table
\item Fig.11: the presentation of the table could be enhanced by reducing the size of columns N, Min, etc. and enlarging the column Distribution to make the graphics visible.
\item p. 17: the full name should be mention for the "A12 effect size test" (i.e. Vargha and Delaney's A12 test, cf. [1])
\item p.17, line 36: "it applies"
\item p.17, line 38: "of" repeated
\item Section 5.6: the last paragraphs about the possible explanations could be regrouped in a separate subsection
\item p.21, line 20: "are" repeated

\begin{quote}{\em 
Reply 2.6: Fixed
}\end{quote}

@@

Reviewer #3: The authors have adequately addressed my observations. Below is a list minor comments (with one exception, all of them are typos).

>>>>

Details:
\bi
\item Page 24:12 - "the cased study"
\item Page 7:24 - "Some studies that report less-than" Remove extra "that".
\item Page 12:41 - "quote elaborate" quite?
\item Page 14:30 - "the of the"
\item Page 14:45 - "complete submitted"
\item Page 15-16 - No thousands separators.
\item Page 16:48 - "only 25\% of the teams…" Was this supposed to be a separate item in the bullet list?
\item Page 18:51 - "raises" to "raised"
\ei
\begin{quote}{\em 
Reply 1.11: Fixed. Thanks!
}\end{quote}

@@

Reviewer \#2: This revised version (R1) of the paper contains many corrections, changes, and enhancements. The authors have considered all the reviewer's comments and have provided precise responses. My own observations (i.e. Reviewer \#2) have been globally satisfied, and thanks to comments from reviewers \#1 and \#3, the paper has been significantly enhanced.

@@

\bi
\item p3, line 1: "that" repeated

\item Section 5.2: the numbers about the TSP database can be regrouped in a table
\item Fig.11: the presentation of the table could be enhanced by reducing the size of columns N, Min, etc. and enlarging the column Distribution to make the graphics visible.
\item p. 17: the full name should be mention for the "A12 effect size test" (i.e. Vargha and Delaney's A12 test, cf. [1])
\item p.17, line 36: "it applies"
\item p.17, line 38: "of" repeated
\item Section 5.6: the last paragraphs about the possible explanations could be regrouped in a separate subsection
\item p.21, line 20: "are" repeated
\ei
\begin{quote}{\em 
Reply 2.6: Fixed
}\end{quote}

@@

Reviewer \#3: The authors have adequately addressed my observations. Below is a list minor comments (with one exception, all of them are typos).
